Market simulator

### 2020-09-22 analysis/05_market_simulator.Rmd
One more time

# # Initial organization configuration
# organization_data <- read_csv(
#   here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
# )
# 
# # Initial persona configuration
# persona_data <- read_csv(
#   here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
# )
```

>>>>

# Initial organization configuration
organization_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
)

# Initial persona configuration
persona_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
)
```
